\section{Problems and Constraints}

\subsection{Problems}

\begin{itemize}
  \item \textbf{Order concurrency} -- Multiple warehouses may attempt to fulfill the same order
    simultaneously, or a customer may place an order that must be split across locations. Without a
    centralized system, there is no reliable way to coordinate stock allocation.
  \item \textbf{Multi-location inventory tracking} -- The company operates three distribution
    warehouses, each carrying a different subset of products. There is currently no unified view of
    what is in stock and where.
  \item \textbf{Shipping and import cost tracking} -- Each warehouse has its own flat shipping and
    import costs. These costs are not systematically recorded, making it difficult to calculate
    total cost of goods sold.
  \item \textbf{ROI calculations} -- Without accurate cost data tied to individual products and
    vendors, the company cannot determine which product lines or import sources are most profitable.
  \item \textbf{Tax and accounting records} -- The company needs detailed, auditable transaction
    history to support tax filings and financial reporting. Current record-keeping is insufficient.
\end{itemize}

\subsection{Constraints}

\begin{itemize}
  \item \textbf{Regulatory constraints} -- Imported food products are subject to federal and state
    regulations. The system must be able to associate products with their country of origin and
    vendor for traceability purposes.
  \item \textbf{Geographic distribution} -- Three separate warehouse locations means the database
    must handle location-specific inventory, shipping costs, and fulfillment logic.
\end{itemize}

\section{Objectives}

\begin{itemize}
  \item Establish a centralized source of truth for inventory, customer, vendor, and transaction data
    across all three warehouse locations.
  \item Minimize data redundancy through normalization to third normal form.
  \item Maintain a detailed, time-variant transaction and invoice history to support accounting and
    auditing needs.
  \item Track product costs including import and shipping expenses to enable accurate profitability
    analysis.
  \item Record customer personal information and purchase history to support customer relationship
    management.
  \item Implement restock threshold tracking so warehouse managers can replenish inventory before
    stockouts occur.
\end{itemize}
