\section{Scope and Boundaries}

The database will cover the sales channel operations of TCD Stocking Inc., including product
catalog management, warehouse inventory, customer records, vendor information, and invoice
processing. The system encompasses three warehouse locations, each carrying a different subset of
the company's product line. Products are organized into categories: Produce, Meat, Dairy, Bakery,
Deli, Frozen, and Shelf-Stable.

The database will \textbf{not} cover employee payroll, human resources, warehouse physical
layout, delivery routing, or marketing operations. Integration with external Customer Relationship
Management software is supported through the customer data model but is outside the scope of
this system.

\section{Business Rules}

\begin{itemize}
  \item Each warehouse stocks zero to many food item types. Not every warehouse carries every product.
  \item Each food item belongs to exactly one product category (Produce, Meat, Dairy, Bakery, Deli,
    Frozen, or Shelf-Stable).
  \item Every product has a restock threshold. When inventory at a warehouse drops below this
    threshold, a warehouse manager initiates a restock from the product's vendor.
  \item A customer can place an order containing many different items at any quantity.
  \item A single order may be fulfilled from more than one warehouse.
  \item Each order has a status: filled, not filled, or unable to be filled.
  \item It is possible for an order to be unfulfillable if sufficient stock does not exist across
    all warehouses.
  \item Each warehouse has a flat shipping cost and a flat import cost associated with it.
  \item Products are sourced from vendors located in East Asia and Latin America. Each product is
    associated with exactly one vendor.
  \item The company must always sell products at a price that exceeds the combined cost of the
    product, import fees, and shipping.
  \item Invoice totals are derived from the line items, quantities, and unit prices on each invoice.
  \item Invoice history must be maintained over time to support accounting and tax reporting.
\end{itemize}
