\section{Individual Reflections}

\subsection*{Ansel}

I was responsible for creating our project presentation as well as finding the appropriate real-world data for our database. This project helped me to exercise the core ideas of database structure, including entity integrity, normalization, and business rules. Working through the project I realized the importance of the planning that goes into designing a database. The more clearly we lay out the structure of our company, the easier it is to implement using SQL.

\subsection*{Anthony}

I was responsible for implementing and testing the database work completed near the end of the project. This included building the MariaDB workflow, loading the data, writing the required SQL outputs, generating the dump file, and making the report match the database that actually exists. The work showed me that a database is strongest when it is plain and exact. Each table needs a clear purpose, and every query should prove something useful about the business.

\subsection*{Jacob}

This project provided me with insight into what is required to go from ideation to implementation of a database in a commercial setting. Specifically, I did not realize how much of the structure of a database is determined by the real-word business rules as opposed to idealized system rules. My responsibilities included scaffolding the structure of the final report, working in tandem with team members to construct the business rules and validate individual cases, construct and document the EERD, and write and test the SQL code that implements the table structure and constraints of the database.
